---
title: "p8105_hw6_cx2257"
author: "Congyang Xie"
date: "12/1/2021"
output: github_document
---

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(readr)
library(modelr)
library(mgcv)
library(patchwork)
```
## Problem 1
```{r}
birthweight_df <- read_csv("https://www.p8105.com/data/birthweight.csv")
skimr::skim(birthweight_df)
```

```{r}
birthweight_df <-
  birthweight_df %>% 
  mutate(
    mrace = fct_infreq(as.factor(mrace)),
    frace = fct_infreq(as.factor(frace)),
    malform = fct_infreq(as.factor(malform)),
    mrace = fct_infreq(as.factor(mrace))
  )
```


```{r}
multi_fit = lm(bwt ~ ., data = birthweight_df)

multi_fit %>% 
  broom::tidy()

step(multi_fit, direction = 'backward')

fit = lm(formula = bwt ~ babysex + bhead + blength + delwt + fincome + 
    gaweeks + mheight + mrace + parity + ppwt + smoken, data = birthweight_df)
```
Backward Elimination Steps:

+ Start with all predictors in the model and then remove the predictor with the highest p-value > $\alpha_{critic}$

+ Re-fit the model and remove the next least significant predictor

+ Done when all non-significant predictors have been removed

```{r}
fit %>% 
  broom::tidy()

birthweight_df %>% 
  add_residuals(fit) %>% 
  add_predictions(fit) %>% 
  ggplot(aes(x = pred, y = resid)) + 
  geom_point(alpha = 0.6, color = "pink") +
  theme_light()
  
```

```{r}
cv_df = 
  crossv_mc(birthweight_df, 100) 

cv_df =
  cv_df %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble))

cv_df = 
  cv_df %>% 
  mutate(
    linear_mod  = map(train, ~lm(formula = bwt ~ babysex + bhead + blength + delwt + fincome + 
    gaweeks + mheight + mrace + parity + ppwt + smoken, data = .x)),
    main_mod  = map(train, ~ lm(bwt ~ blength + gaweeks, data = .x)),
    side_mod  = map(train, ~ lm(bwt ~ bhead + blength + babysex, data = .x))) %>% 
  mutate(
    rmse_linear = map2_dbl(linear_mod, test, ~rmse(model = .x, data = .y)),
    rmse_smooth = map2_dbl(main_mod, test, ~rmse(model = .x, data = .y)),
    rmse_wiggly = map2_dbl(side_mod, test, ~rmse(model = .x, data = .y)))
```

```{r}
cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse) ) + 
  geom_violin(width = 1.4) +
  geom_boxplot(width = 0.1,
               color = "grey",
               alpha = 0.2) +
  theme_light()
```

## Problem 2


```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```
```{r}
lm(tmin ~ tmax, data = weather_df) %>% 
  broom::glance() %>% 
  pull(r.squared)
```

```{r}
weather_stat =
  weather_df %>%
  modelr::bootstrap(n = 5000) %>%
  mutate(
    models = map(strap, ~ lm(tmax ~ tmin, data = .x)),
    results = map(models, broom::tidy),
    r_sqr = map(models, broom::glance)
  ) %>%
  select(.id, results, r_sqr) %>%
  unnest(r_sqr) %>%
  select(.id, r.squared, results) %>%
  unnest(results) %>%
  group_by(.id) %>%
  mutate(estimate2  = lead(estimate, n = 1),
         lg_product = log10(estimate * estimate2)) 

r_sqr_plt = weather_stat %>%
  drop_na() %>%
  select(.id, r.squared) %>%
  ggplot(aes(x = r.squared)) + geom_density() +
  theme_light()

lg_plt =
  weather_stat %>%
  drop_na() %>%
  select(.id, lg_product) %>%
  ggplot(aes(x = lg_product)) + geom_density() +
  theme_light()

r_sqr_plt + lg_plt
```

r square reaches the most likelihood around 0.914. log product reaches the most likelihood around 0.874.

```{r}
weather_stat %>% 
  drop_na() %>% 
  ungroup() %>% 
  select(r.squared) %>% 
  summarize(
    ci_lower = quantile(r.squared, 0.025), 
    ci_upper = quantile(r.squared, 0.975)) %>% 
  knitr::kable(digits = 3)

weather_stat %>% 
  drop_na() %>% 
  ungroup() %>% 
  select(lg_product) %>% 
  summarize(
    ci_lower = quantile(lg_product, 0.025), 
    ci_upper = quantile(lg_product, 0.975)) %>% 
  knitr::kable(digits = 3)
```

